### 2019-12-12 ch1_introduction/content.tex
update

\newpage 
\section{Hippocratic oath for method developers}
Before setting out on this perilous journey, I write a Hippocratic oath which I believe all developers of computational tools should swear by before haphazardly developing and publishing new software tools.

>>>>

\newpage 
\section{Hippocratic oath for method developers}
Before setting out on this perilous journey (i.e. the rest of this dissertation), I wrote a Hippocratic oath which I believe all developers of computational tools should swear by before haphazardly developing and publishing new software tools.
